Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-08 paper/manuscript.tex

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.
JS: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.
MK: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.
DLM: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.
GT: Contributed to introduction and drug discovery sections, and helped edit the paper.
AR: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:step2}, and helped edit the paper.
MRS: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.
LNN: Helped write the simulation length, stopping conditions, and information saving section.
BA: \todo[inline, color={red!20}]{@Bryce insert info here}
JM: \todo[inline, color={red!20}]{@Julien insert info here}
JDC: \todo[inline, color={red!20}]{@JDC insert info here}
HX: \todo[inline, color={red!20}]{@Huafeng insert info here}
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

>>>>

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and co-designed figures ~\ref{} and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.
JS: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.
MK: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.
DLM: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.
GT: Contributed to introduction and drug discovery sections, and helped edit the paper.
AR: Created figure~\ref{fig:freeenergytrajectories}, contributed to section \ref{sec:step2}, and helped edit the paper.
MRS: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations.
LNN: Helped write the simulation length, stopping conditions, and information saving section.
BA: \todo[inline, color={red!20}]{@Bryce insert info here}
JM: Contributed to sections~\ref{subsec:reproducible},~\ref{sec:step1},~\ref{} 4.2, 5.3, 6, 8.3.1, 8.3.2\todo[inline, color={red!20}]{@Julien insert info here}
JDC: \todo[inline, color={red!20}]{@JDC insert info here}
HX: \todo[inline, color={red!20}]{@Huafeng insert info here}
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.
